\begin{thebibliography}{99}

\bibitem{cebaf} 
C.W. Leemann, D.R. Douglas and G.A. Krafft,
\newblock Annu. Rev. Nucl. Part. Sci. {\bf 51} (2001) 413.

\bibitem{CLAS} B.A. Mecking {\em et~al.},
\newblock Nucl. Instr. and Meth. {\bf A 503} (2003) 513.

\bibitem{Gep} M.K. Jones {\em et~al.},
\newblock Phys. Rev. Lett. {\bf 84} (2000) 1398.

\bibitem{Gmn} W. Xu {\em et~al.}, 
\newblock Phys. Rev. Lett. {\bf 85} (2000) 2900.

\bibitem{VCS} JLab experiment E93-050,
\newblock P. Bertin and G. Fournier, spokespersons.

\bibitem{RCS} JLab experiment E99-114,
\newblock C. Hyde-Wright, A. Nathan and B. Wojtsekhowski, spokespersons.

\bibitem{NDelta} JLab experiment E91-011,
\newblock S. Frullani, J. Kelly and A. Sarty, spokespersons.

\bibitem{parity} K.A. Aniol {\em et~al.}, 
\newblock Phys. Lett. {\bf B 71} (2001) 959.

\bibitem{vernin} P. Vernin,
\newblock Research Program at CEBAF, Vol. II, 615 (1986).

\bibitem{brown}  K.L. Brown,
\newblock SLAC Report 75 (1970), revised edition, 1982, unpublished.

\bibitem{CDR} The CEBAF Hall A Collaboration,
\newblock Conceptual Design Report:
Basic Experimental Equipment, A7 Detector Systems, 1990, unpublished.

\bibitem{schneider} W.J. Schneider {\it et al.}, 
\newblock Adv. Cryogenic Engineering {\bf 41} (1996) 669.

\bibitem{r1} EPICS documentation,
\newblock {\tt www.aps.anl.gov/epics}.

\bibitem{danfysik} Danfysik A/S,
\newblock Mollehaven 31, DK-4040 Jyllinge, Denmark, {\tt www.danfysik.dk}.

\bibitem{FuG} F. u. G. Elektronik GmbH,
\newblock Florianstrasse 2, D-83024 Rosenheim, Germany, {\tt www.fug-elektronik.de}.

\bibitem{dynapower} Dynapower Corporation,
\newblock P.O. Box 9210, South Burlington, VT 05407, USA, {\tt www.dynapower.com}.

\bibitem{vernin2} P. Vernin {\em et~al.}, 
\newblock Nucl. Instr. and Meth.  {\bf A 449} (2000) 505.

\bibitem{Metrolab} Metrolab Instruments SA,
\newblock 110 Ch. du Pont du Centenaire, CH-1228 Plan-les-Ouates, 
Geneva, Switzerland.

\bibitem{Lakeshore} Lake Shore Cryotronics Inc.,
\newblock 575 McCorkle Blvd., Westerville, OH 43082-8888, USA. 

\bibitem{HP} Hewlett Packard,
\newblock Palo Alto, CA, USA, {\tt www.hp.com}.

\bibitem{WhitingCrane} Whiting Corporation,
\newblock 26000 Whiting Way, Monee, IL 60449, USA. 

%\bibitem{vxworks} Wind River Systems Inc.,
%\newblock Alameda, CA, USA, {\tt www.windriver.com}.

\bibitem{AppliedGeo} Applied Geomechanics Incorporated,
\newblock 1336 Brommer Street, Santa Cruz, CA 95062, USA, model 711-2.

\bibitem{A_P} K.A. Aniol and V. Punjabi,
\newblock Hall A Line of Sight 
Shielding, JLab-TN-91-024 (1991).

\bibitem{geant} GEANT, Detector description and simulation tool, CERN 
Program Library W5013, {\tt wwwinfo.cern.ch/asd/geant/}.

\bibitem{DESY} G. Bathow, E. Freytag, and K. Tesh,
\newblock Nucl. Phys. {\bf B 2} (1967) 669.

\bibitem{SLAC} A.M. Boyarski {\em et~al.},
\newblock C.2 Yields of Secondary Particles from 18 GeV Electrons, 
SLAC report, 1968.

\bibitem{vdcNIM} 
K.G. Fissum {\em et~al.},
\newblock Nucl. Instr. and Meth. {\bf A 474} (2001) 108; Vertical Drift Chambers for the Hall A High Resolution
Spectrometers at Jefferson Lab, JLab-TN-00-016 (2000). 

\bibitem{LeCroy} LeCroy Corporation,
\newblock Chestnut Ridge, NY 10977-6499, USA, {\tt www.lecroy.com}.

\bibitem{multsc} J.~LeRose,
\newblock Report on Studies of the Effect on Resolution of the Exit 
Window of the HRS Spectrometers in Hall A, 
JLab-TN-00-001 (2000).

\bibitem{Bicron} Bicron Newbury,
\newblock 12345 Kinsman Road, Newbury, OH 44065-9577, USA.

\bibitem{Burle} Burle Electron Tubes,
\newblock 1000 New Holland Ave., Lancaster, PA 17601-5688, USA.

\bibitem{Photonis} Photonis,
\newblock Avenue Roger Roncier, Z.I. Beauregard, 
B.P. 520, 19106 Brive Cedex, France.

\bibitem{gascher} M. Iodice {\em et~al.},
\newblock Nucl. Instr. and Meth. {\bf A 411} (1998) 223.

\bibitem{lightmirror} F. Garibaldi {\em et al.},
\newblock Lightweight mirrors for \v{C}erenkov detectors, 
to be submitted to Nucl. Instr. and Meth.

\bibitem{pope} M. Shepherd and A. Pope,
\newblock Investigation of BURLE 8854 photomultiplier tube,
JLab-TN-97-028 (1997). 

\bibitem{shower} A. Ketikyan {\em et~al.},
\newblock Lead Glass Total Absorption Shower Detector, hallaweb.jlab.org/equipment/detectors/detectors.html.

\bibitem{Airglass} Airglass AB,
\newblock BOX 150, 245 22 Staffanstorp, Sweden. 

\bibitem{mirraero} E.J. Brash {\em et~al.},
\newblock Nucl. Instr. and Meth. {\bf A 487} (2002) 346.

\bibitem{a1a2} M. Coman,
\newblock M.S. thesis, Florida International University,
Miami (2000);  B. Wojtsekhowski {\em et~al.}, High performance 
threshold aerogel counters, to be submitted to Nucl. Instr. and Meth.

\bibitem{perrino} R. Perrino {\em et~al.}, 
\newblock Nucl. Instr. and Meth. {\bf A 457} (2001) 571.

\bibitem{lagamda} L. Lagamda {\em et~al.},
\newblock Nucl. Instr. and Meth. {\bf A 471} (2001) 325.

\bibitem{iommi} R. Iommi {\em et~al.},
\newblock Test and Development of a \v{C}erenkov diffusion detector 
prototype using Airglass aerogel at TJNAF, JLab-TN-00-010 (2000).


\bibitem{Matsu} Matsushita Electric Works,
\newblock {\tt www.mew.co.jp}.

\bibitem{fppnim} V. Punjabi {\em et~al.},
\newblock submitted to Phys. Rev. C.

\bibitem{gayou} O. Gayou {\em et~al.},
\newblock Phys. Rev. C {\bf 64} (2001) 38202.

\bibitem{EVA} M. Kmit {\em et al.},
\newblock Brookhaven Internal Report EP{\&}S91-4.

\bibitem{COSY} M. Berz, H.C. Hoffmann and H.Wollnik,
\newblock Nucl. Instr. and Meth. {\bf A 258} (1987) 402.

\bibitem{opman} Hall A Operations Manual,
\newblock {\tt hallaweb.jlab.org/document/OPMAN/}.

\bibitem{dump} C.K. Sinclair,
\newblock Design criteria for beam dumps for Halls A and C, JLab-TN-92-064 (1992).

\bibitem{barry} W. Barry {\em et al.},
\newblock Beam position measurement in 
the CEBAF recirculating linacs by use of pseudorandom pulse sequences, 
JLab-TN-90-246 (1990); 
Basic noise considerations for CEBAF beam position monitors, 
JLab-TN-91-087 (1991).

\bibitem{kazimi} R. Kazimi {\it et al.}, Proc. of Particle Accelerator 
Conference,  IEEE {\bf 0-7803-3503} (1996) 2610. 

\bibitem{unser} K. Unser, 
\newblock IEEE Transactions on Nuclear Science, {\bf 28} (1981) 2344. 

\bibitem{berthot} J. Berthot and P. Vernin, 
\newblock Nucl. Phys. News {\bf 9} (1990) 12.

\bibitem{marchand} D. Marchand,
\newblock Ph.D. thesis, University of Blaise Pascal, Clermont-Ferrand (1997).

\bibitem{ravel} O. Ravel,
\newblock Ph.D. thesis, University of Blaise Pascal, Clermont-Ferrand (1997).

\bibitem{moller} A.A. Kresnin and L.N. Rozentsveig,
Sov. Phys. JETP {\bf 5} (1957) 288.

\bibitem{Cpt_CDR} M.~Baylac {\em et~al.},
\newblock Phys. Lett. {\bf B 539} (2002) 8.

\bibitem{Cpt_Damien} D.~Neyret {\em et al.},
\newblock Nucl. Instr. and Meth. {\bf A 443} (2000) 231.

\bibitem{Cpt_Cavity} J.P.~Jorda {\em et~al.},
\newblock Nucl. Instr. and Meth. {\bf A 412} (1998) 1;
 N.~Falletto {\it et al.}, Nucl. Instr. and Meth. {\bf A 459} (2001) 412.

\bibitem{Cpt_Steffie} S.~Escoffier,
\newblock Doctorate thesis, University of Paris 7, Denis Diderot (2001),
{\tt hallaweb.jlab.org/compton/Documentation/Papers/index.php}.

\bibitem{Allen-Bradley} Allen-Bradley,
\newblock {\tt www.ab.com}.

\bibitem{Oxford} Oxford Instruments Superconducting Technology,
\newblock 600 
Milik Street, PO Box 429, Carteret, NJ 07008-0429, USA.

\bibitem{cryoweb}{\tt hallaweb.jlab.org/equipment/targets/cryotargets/Halla$\_$tgt.html}. 

\bibitem{cryonim} JLab Cryotarget System,
\newblock to be submitted to Nucl. Instr. and Meth.  

\bibitem{GDH} M. Amarian {\em et al.},
\newblock Phys. Rev. Lett. {\bf 89} (2002) 242301.

\bibitem{A1n} JLab experiment E99-117,
\newblock J.-P. Chen, Z.-E. Meziani and P. Souder, spokespersons.

\bibitem{g2n} JLab experiment E97-103,
\newblock T. Averett and W. Korsch, spokespersons.

\bibitem{SGDH} JLab experiment E97-110,
\newblock G. Cates, J.-P. Chen and F.  Garibaldi, spokespersons.

\bibitem{duality} JLab experiment E01-012,
\newblock J.-P. Chen, S. Choi and N. Liyanage, spokespersons.

\bibitem{12gev} {\it The Science Driving the 12 GeV Upgrade of CEBAF},
\newblock White Paper prepared for the NSAC Long Range Plan, edited by L.S. 
Cardman {\em et al.}, {\tt www.jlab.org/div$\_$dept/physics$\_$division/GeV/WhitePaper$\_$V11.pdf}.

\bibitem{Principle} M.A. Bouchiat, T.R. Carver and C.M. Varnum,
\newblock Phys. Rev. Lett. {\bf 5} (1960) 373; N.D. Bhaskar, W. Happer, and T. McClelland, 
Phys. Rev. Lett. {\bf 49} (1982) 25;
W. Happer {\it et al.}, Phys. Rev. A {\bf 29} (1984) 3092.

\bibitem{SLACnew} P.L. Anthony {\em et al.},
\newblock Phys. Rev. Lett. {\bf 71} (1993) 959.

\bibitem{torlon} 
{\tt www.portplastics.com/plastics/high$\_$perform/torlon.html}.

\bibitem{rate} T.E. Chupp {\em et al.}, 
\newblock Phys. Rev. C {\bf 36} (1987) 2244.

\bibitem{beam} K.P. Coulter {\em et al.},
\newblock  Nucl. Instr. and Meth.  {\bf A 276} (1989) 29.

\bibitem{dipole} N.R. Newbury {\em et al.},
\newblock  Phys. Rev. A {\bf 48} (1993) 4411.

\bibitem{field} G.D. Cates {\em et al.},
\newblock Phys. Rev. A {\bf 38} (1988) 5092.

\bibitem{corning} Corning Inc.,
\newblock One Riverfront Plaza, Corning, NY 14831, USA, {\tt www.corning.com}.

\bibitem{ge} General Electric Components Marketing and Sales Operation,
\newblock 1975 Noble Road, Nela Park, Cleveland, OH 44112, USA, {\tt www.ge.com}.

\bibitem{Coherent} FAP-I system,
\newblock Coherent Inc., 5100 Patrick Henry Drive, Santa Clara, CA 95054, USA, {\tt www.cohr.com}.

\bibitem{afp} A. Abragam,
\newblock {\it Principles of Nuclear Magnetism}, 
Oxford University Press, New York, 1961.

\bibitem{labview} National Instruments, 
\newblock {\tt sine.ni.com}.

\bibitem{targ} 
S. Jensen,
\newblock Ph.D. thesis, Caltech (2000); I. Kominis, Ph.D. thesis, 
Princeton University (2000); Hall A polarized $^3$He collaboration, Nucl. 
Instr. and Meth. in preparation; {\tt www.jlab.org/e94010}.

\bibitem{ref1} N. Voegler {\em et al.},
\newblock Nucl. Instr. and Meth. {\bf 198} (1982) 
293.

\bibitem{ref2} F. Garibaldi {\em et al.}, 
\newblock Nucl. Instr. and Meth. {\bf A 314} (1992) 1. 

\bibitem{e89003} J. Gao {\em et al.},
\newblock Phys. Rev. Lett. {\bf 84} (2000) 3265; 
N. Liyanage {\it et al.}, Phys. Rev. Lett. {\bf 86} (2001) 5670.

\bibitem{e89033} S. Malov {\em et al.},
\newblock Phys. Rev. C {\bf 62} (2000) 057302.

\bibitem {ref16O} JLab experiment E00-102,
\newblock A. Saha, W. Bertozzi, L.B. Weinstein and K.G. Fissum, spokespersons.

\bibitem{ref4} JLab experiment E94-107,
\newblock F. Garibaldi {\it et al.}, spokespersons.

\bibitem{ref5} E. Cisbani {\it et al.}, A waterfall target system for 
Hall A at Jefferson Lab, INFN/ISS 97/04.

\bibitem{r2} A list of projects using EPICS can be found at
{\tt csg.lbl.gov/EPICS/EPICS\_Sites.html}.

\bibitem{r3} Documentation on the MVME162 can be found at
{\tt www.mcg.mot.com}.

\bibitem{r4}
Wind River,
\newblock Alameda, CA, USA, {\tt www.wrs.com}.

\bibitem{tcl} Tool Command Language,
{\tt www.tcl.tk}.

\bibitem{coda} W.A. Watson {\em et al.},
\newblock  CODA: A Scalable,
Distributed Data Acquisition System, in {\em Proc. of the
Real Time 1993 Conference}, p. 296;  
G. Heyes {\em et al.}, The CEBAF on-line data
acquisition System, in {\it Proc. of the CHEP Conference}, 1994,
p. 122; 
G. Heyes {\em et al.}, Real-time
Front End Software for CODA, in {\em Proc. of the Real Time
1993 Conference}, p. 382;  
D.J. Abbott {\it et al.}, CODA Performance in the Real World,
{\it 11th IEEE NPSS Real Time 1999 Conference}, JLab-TN-99-12 (1999).

\bibitem{silo} Manufactured by StorageTek Inc.,
\newblock Louisville, CO, USA, {\tt www.storagetek.com}.

\bibitem{sunos} Developed by SUN Microsystem,
\newblock {\tt www.sun.com}.

\bibitem{linux} LINUX Software distributed by Red Hat Software Inc.,
\newblock Durham, N.C., USA, {\tt www.redhat.com}.

\bibitem{trigsuper} E. Jastrzembski {\em et al.}, 
\newblock The Jefferson Lab Trigger Supervisor System, {\it 11th IEEE NPSS Real Time 1999
Conference}, JLab-TN-99-13 (1999).

\bibitem{paw} Physics Analysis Workstation,       
\newblock  {\tt wwwasd.web.cern.ch/wwwasd/paw/}. 

\bibitem{root} R. Brun and F.  Rademakers, 
\newblock ROOT --- An Object-Oriented Data Analysis 
Framework, {\it Proc. AIHENP'96 Workshop}, Lausanne, Sep.  1996, 
Nucl. Instr. and Meth. {\bf A 389} (1997) 81.

\bibitem{jlabfarm} Jefferson Lab Scientific Computing Overview,      
\newblock {\tt cc.jlab.org/scicomp/overview/}.

\bibitem{espace} E.A.J.M.~Offerman,
\newblock ESPACE User's Guide, {\tt hallaweb.jlab.org/espace/docs.html}.

\bibitem{cernlib} CERN Program Library,      
\newblock {\tt wwwasd.web.cern.ch/wwwasd/cernlib.html}. 

\bibitem{hbook} HBOOK -- Statistical Analysis and Histogramming, 
\newblock CERN Program Library Long Writeup Y250,      
{\tt wwwasdoc.web.cern.ch/wwwasdoc/hbook/HBOOKMAIN.html}.

\bibitem{kuip} KUIP -- Kit for a User Interface Package, 
\newblock
{\tt wwwasdoc.web.cern.ch/wwwasdoc/kuip/kuipoverview.html}.

\bibitem{coolhands} 
J.\ B.\ Mandeville, 
\newblock Ph.D. thesis, University of Illinois at 
Urbana-Champaign (1993).

\bibitem{wechsler} R. H.  Wechsler,
\newblock B.S. thesis, Massachusetts Institute 
of Technology (1996).

\bibitem{garfield} {\tt garfield.web.cern.ch/garfield/}.

\bibitem{bevington} P.~R.~Bevington,
\newblock Data Reduction and Error Analysis for the Physical 
Sciences, McGraw Hill, New York, 1969.

\bibitem{hallaroot} The 
Hall A ROOT Project, {\tt hallaweb.jlab.org/root}.

\bibitem{optim} {\tt hallaweb.jlab.org/root/optimize++}.

\bibitem{nilanga1}  N. Liyanage,
\newblock Optics Calibration of the Hall 
A High-Resolution Spectrometers using the new C++ Optimizer, 
JLab-TN-02-012 (2002).

\bibitem{tn_epscan} P.E. Ulmer, H. Ibrahim and N. Liyanage, 
\newblock Calibration of Beam Energy and Spectrometer Central Angles using Hall
A HRS in $^1$H($e,e^\prime p$), JLab-TN-00-024 (2000).

\bibitem{tn_epscan2} H. Ibrahim, P.E. Ulmer and N. Liyanage, 
\newblock Calibration of Spectrometer Central Angles using Hall A HRS in
$^1$H($e,e^\prime p$), JLab-TN-02-032 (2002).

\bibitem{nilanga2}  N. Liyanage, 
\newblock Spectrometer Constant Determination for the Hall A HRS pair, 
JLab-TN-01-049 (2001).

\bibitem{Levchuk:1992np}
L.~G.~Levchuk,
\newblock Nucl. Instr. and Meth. {\bf A 345} (1994) 496.
\end{thebibliography}

